The Galactic Midplane is Not a Plane: Implications for {\em Gaia}

### 2019-04-22 paper/ms.tex
added M-M grant

Add sentences about distribution function modeling

@@

\acknowledgments
We would like to thank Megan Bedell, Tobias Buck, David W. Hogg, and Kathryn
Johnston for many useful discussions. A.B. would like to thank Todd Phillips
for helpful discussions. A.B. was supported in part by the Roy \& Diana
Vagelos Program in the Molecular Life Sciences and the Roy \& Diana Vagelos
Challenge Award. The work of \Gus{everyone} is supported by the Simons
Foundation. \Gus{remove last sentence if everyone CCA affiliated}

>>>>

{\bf Add sentences about distribution function modeling}

@@

\acknowledgments
We would like to thank Megan Bedell, Tobias Buck, and Todd Phillips
%mm [moving to author list] David W. Hogg, and Kathryn
%Johnston 
%for many useful discussions. A.B. would like to thank Todd Phillips
for helpful discussions. A.B. was supported in part by the Roy \& Diana
Vagelos Program in the Molecular Life Sciences and the Roy \& Diana Vagelos
Challenge Award. 
%mm The work of \Gus{everyone} is supported by the Simons
%Foundation. \Gus{remove last sentence if everyone CCA affiliated}
M.-M.M.L. was partly supported by NSF grant AST18-15461.
